Questions regarding modeling

### 2020-09-27 Questions.Rmd
Updated "Questions" file

After reading the book from Krushke and going back and forth between the "time-varying-anova-example" file and the Stan model "time-varying" there are certain things that I still don't understand:

1. Krushke uses diagrams (like one below) to illustrate how models are built
```{r Fig 1., echo=FALSE, fig.cap="Krushke's diagram for two groups, metric response analysis", out.width='60%'}
knitr::include_graphics("Diagram Krushke.png")
```

From what I have understood,in the diagram the response is expected to come from a $t$ distribution where the three parameters $\nu,\mu$ and $\sigma$.
The examples I have seen on Krushke using Stan following something like this:

@@

where $\epsilon_n \sim normal(0,\sigma)$ 
or \[y_n \sim normal(\alpha+\beta x_n,\sigma)$ $(2)\]

@@

I know you have mentioned this before, but I am a little confused by how the argument is passed in the model in "time-varying.stan". The parameter $\beta$ is a matrix of 6 rows and two columns, and then is transformed into $\mu$, another matrix with row number equal to the total number of observations and 2 columns. And each $\mu$ is a combination of the basis functions of the spline and the $\beta$ parameter.

When the final model is specified,I don't fully understand how the model would look if specified as in $1$.

>>>>

After reading the book from Krushke and going back and forth between the "time-varying-anova-example" file and the Stan model "time-varying" there are certain things that I have understood:

* The specification of prior distributions: I did not understand at the beginning why you chose a Cauchy distribution for the error, but upon reading and talking with you I understand it is just a possible distribution, it has large tails and therefore can accomodate outliers well.

* I also understand most of the operations that take place and specially for the simulate_data function.

Things that I still don't understand:

1. Krushke's book uses Stan model specification that goes something like this:

@@

where $\epsilon_n \sim normal(0,\sigma)$. 
Alternatively, the model can be specified as:
\begin{align}
y_n \sim normal(\alpha+\beta x_n,\sigma) \tag{2}\\
\end{align}

@@

I understand this is a less complex model than the one that we are implementing, but the correspondence between the model notation and the specification in Stan makes it easy to understand for people that don't know complex statistical notation (such as myself).

I know you have mentioned this before, but I am a little confused by how the argument is passed in the model in "time-varying.stan". The parameter $\beta$ is a matrix of 2 rows and 6 columns, and then is transformed into $\mu$, by multiplying $\beta$ (2 rows,6 columns) by  matrix $X$ (6 rows, 5 columns) .In this way, $\mu$ is a combination of the basis functions of the spline and the $\beta$ parameter, with size ( 2 rows, 5 columns).

But I looked upon the basis spline functions that the script creates (X_bs) and while I think I understand what X_bs is(a matrix that contains a basis function for a spline model on each column), I don't understand the role of this matrix in the Bayesian model. Does this mean that we are using X_bs to fit the data? And if that is the case, setting a different seed then would cause to have a better or worse fit?

When the final model is specified,I don't fully understand how the model would look if specified as in $(1)$.It is running within a loop, and if taken literally, the model is:

\begin{align}
y_i \sim normal(\mu(time_i,treatment_i)) \tag{3}\\
\end{align}
Does this mean the model specifies an interaction between the $time$ and $treatment$ factors? I think this is the most important thing that I don't understand, because when the model is run and the "mu_post" variable is called in the R script, I just seen 100 matrices each size (2,5) but don't understand how the model created the numbers in each cell.

Thank you for your help, if you can provide some guidance on the questions I wrote here, that would be very helpful!
